### 2015-12-14 paper/4-performance.tex
Proofread section 4.1

\subsection{Benchmarks}
We use a selection of benchmarks, based on those found in the literature.
Three different types of benchmark are defined:
\begin{enumerate}
    \item The \textit{Queue} model, based on the HI model of DEVStone~\cite{DEVStone}, creates a chain of hierarchically nested atomic \textsf{DEVS} models.
          A single generator will push events into the queue, which get processed by the processors after a fixed or random delay.
          It takes two parameters: width and depth, which determine the width and depth of the hierarchy.
          This benchmark shows how the complexity of the simulation kernel behaves for an increasing amount of atomic models, and an increasingly deep hierarchy.
          An example for width 2 and depth 3 is shown in Figure~\ref{fig:queue_model}.

    \item The \textit{PHOLD} model, presented by~\cite{PHOLD}, creates $n$ atomic models, where each model has exactly $n-1$ output ports.
          Couplings are made to directly connect each atomic model to every other atomic model.
          After a random delay, atomic models will send out an event to a randomly selected output port.
          Output port selection happens in two phases: first it is decided whether the event should be sent to an atomic model inside or outside of this coupled model.
          Afterwards, a uniform selection is made between the remaining ports.
          The model takes one parameter: the percentage of remote events, which determines the fraction of messages routed to other coupled models.
          This benchmark shows how the simulation kernel behaves in the presence of many local or remote events.
          An example for four models, split over two nodes, is shown in Figure~\ref{fig:PHOLD_model}.

    \item The \textit{HighInterconnect} model, a merge of the HI model of DEVStone~\cite{DEVStone} and PHOLD~\cite{PHOLD}, creates $n$ atomic models, where each model has exactly one output port.
          All models are still connected to one another, but all over the same port: every model will receive a generated event.
          The model takes one parameter: the number of models.
          This benchmark investigates the complexity of the event routing algorithm, and how the simulation kernel handles many simultaneous events.
          An example for four models is shown in Figure~\ref{fig:interconnect_model}.
\end{enumerate}

We opted to deviate from the DEVStone benchmark, as DEVStone tends towards unrealistic models since most transitions occur simultaneously.
In all of our benchmark models, simultaneous internal transitions are avoided as much as possible through the use of a random time advance.
DEVStone also uses an artificial load function, which easily skews the result: the simulation kernel overhead is dominated by the artificial load.

>>>>

\subsection{Benchmarks}
We use three different benchmarks, which cover different aspects of the simulation kernel:
\begin{enumerate}
    \item The \textit{Queue} model, based on the \textit{HI} model of DEVStone~\cite{DEVStone}, creates a chain of hierarchically nested atomic \textsf{DEVS} models.
          A single generator pushes events into the queue, which are processed by the processors after a random delay.
          It takes two parameters: width and depth, which determine the width and depth of the hierarchy.
          This benchmark shows how the complexity of the simulation kernel behaves for an increasing amount of atomic models, and an increasingly deep hierarchy.
          An example for width 2 and depth 3 is shown in Figure~\ref{fig:queue_model}.

    \item The \textit{PHOLD} model, presented by~\cite{PHOLD}, creates $n$ atomic models, where each model has exactly $n-1$ output ports.
          Each atomic model is directly connected to every other atomic model.
          After a random delay, an atomic model sends out an event to a randomly selected output port.
          Output port selection happens in two phases: first it is decided whether the event should be sent to an atomic model at the same node.
          Afterwards, a uniform selection is made between the remaining ports.
          The model takes one parameter: the percentage of remote events, which determines the fraction of messages routed to other nodes.
          This benchmark shows how the simulation kernel behaves in the presence of many local or remote events.
          An example for four models, split over two nodes, is shown in Figure~\ref{fig:PHOLD_model}.

    \item The \textit{HighInterconnect} model, a merge of PHOLD~\cite{PHOLD} and the \textit{HI} model of DEVStone~\cite{DEVStone}, creates $n$ atomic models, where each model has exactly one output port.
          Similar to PHOLD, all models are connected to one another, but all through the same port: every model receives each generated event.
          The model takes one parameter: the number of models.
          This benchmark investigates the complexity of event routing, and how the simulation kernel handles many simultaneous events.
          An example for four models is shown in Figure~\ref{fig:interconnect_model}.
\end{enumerate}
